\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-06-27 paper/ms.tex
Comparison to other packages

>>>>

\section{Relation to Other Algorithms}\label{sec:relation}
The simple C implementation of Nested Sampling given by
\citet{skilling2006nested}

\pkg{MultiNest} \citep{feroz2009multinest} is a Nested Sampling implementation
that dispenses with MCMC for generating new particles from constrained
prior distributions. Instead, the new particles are generated by making
an approximation to the constrained prior using ellipses. This tends to work
well in low to moderate dimensional parameter spaces (up to $\sim 50$).
In higher dimensions, \pkg{DNest4} is more useful than \pkg{MultiNest}
since it is based on MCMC. We expect \pkg{MultiNest} to be more useful
than
\pkg{DNest4} only on low to moderate dimensional problems with slow
likelihood evaluations.

\pkg{emcee} \citep{emcee}

The popular \pkg{JAGS} \citep{jags} and \pkg{Stan} \citep{stan} packages
are more convenient than \pkg{DNest4} for specifying models, by virtue
of their model-specification languages. However, being based on Gibbs
sampling and Hamiltonian MCMC respectively, they can run into difficulty
on multimodal posterior distributions. Also, they do not calculate
marginal likelihoods.
